---
title: "ACT Analysis"
author: "Steven Macapagal"
date: "6/6/2022"
output: html_document
---

## Notebook setup

* Filename: 01-act-analysis.Rmd
* Path: ./src/01-act-analysis.Rmd
* Author: Steven Macapagal
* Date created: 2022-06-06
* Date modified: 2022-07-12
* Purpose: This notebook preps and conducts analysis ACT data for Question 3.
* Inputs: df_act
* Outputs: 
* Notes:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ACT data at a glance

```{r}
glimpse(df_act)
```

## ACT data summaries

```{r}
df_act %>%
  group_by(GradeLevelTaken) %>%
  summarize(n = n(),
            MeanScience = mean(Science, na.rm = TRUE))
```


```{r}
df_act_attendees %>%
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(GradeLevelID) %>%
  summarize(n = n(),
            MeanScience = mean(Science, na.rm = TRUE))
```


```{r}
df_act_survey_takers %>%
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(GradeLevelID) %>%
  summarize(n = n(),
            MeanScience = mean(Science, na.rm = TRUE))
```


```{r}
dist_act_survey_takers <- df_act_survey_takers %>%
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(GradeLevelID,
           CRDoseGroup) %>%
  summarize(n = n(),
            MeanScience = mean(Science, na.rm = TRUE))
```

Next, test for normality. It appears from the histogram and the Shapiro-Wilk tests that the populations seem relatively normal.

* p-value for 0-2 visits = 0.3553
* p-value for 2+ visits = 0.4434

```{r normality_checks}

df_act_survey_takers %>%  
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE)) %>%
  ungroup() %>%
  ggplot() +
  geom_histogram(aes(x = Science)) +
  facet_wrap(~ CRDoseGroup)


df_act_survey_takers %>%  
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE),
         CRDoseGroup == "0-2 Visits") %>%
  ungroup() %>%
  pull(Science) %>%
  shapiro.test()

```

Next, test for homogeneity of variances.

```{r homoskedasticity, warning=FALSE}
df_act_survey_takers %>%  
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE),
         GradeLevelID == 11) %>%
  ungroup() %>%
  bartlett.test(Composite ~ CRDoseGroup, data = .)

df_act_survey_takers %>%  
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE),
         GradeLevelID == 12) %>%
  ungroup() %>%
  bartlett.test(Composite ~ CRDoseGroup, data = .)
```

The p-value for 11th grade is 0.2208 and for 12th grade is 0.6013. Thus, it seems the variances are the same between Camp Rio groups per grade level.

Therefore, we will use a pooled t-test.

* H0: There is no difference in ACT score between small dosage and large dosage Camp Rio groups.
* Ha: There is a difference.

```{r t_test, warning=FALSE}
df_act_survey_takers %>%  
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE),
         GradeLevelID == 11) %>%
  ungroup() %>%
  t.test(Composite ~ CRDoseGroup, data = .,
         var.equal = TRUE)

df_act_survey_takers %>%  
  filter(GradeLevelID %in% c(10, 11, 12)) %>%
  group_by(StudentNumber) %>%
  filter(GradeLevelTaken == max(GradeLevelTaken, na.rm = TRUE),
         Science == max(Science, na.rm = TRUE),
         GradeLevelID == 12) %>%
  ungroup() %>%
  t.test(Composite ~ CRDoseGroup, data = .,
         var.equal = TRUE)
```

Given that the p-value is 0.00169 and 0.01049 for 11th and 12th grade, respectively, it appears the ACT scores are different per group.