---
title: "GPA analysis"
author: "Steven Macapagal"
date: "6/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Notebook setup

* Filename: 04-gpa-analysis.Rmd
* Path: ./src/04-gpa-analysis.Rmd
* Author: Steven Macapagal
* Date created: 2022-06-14
* Date modified: 2022-06-14
* Purpose: This notebook preps and conducts analysis for GPA data for Question 3.
* Inputs: df_gpa_all_attendees, df_gpa_survey_takers
* Outputs: 
* Notes:

## Analysis of all GPAs

```{r}
raw_gpa %>%
  group_by(GradeLevelID) %>%
  summarize(n = n(),
            MeanGPA = mean(CumulativeGPA, na.rm=TRUE))
```

## Analysis of Camp Rio attendees

```{r}
df_gpa_attendees %>%
  group_by(GradeLevelID) %>%
  summarize(n = n(),
            MeanGPA = mean(CumulativeGPA, na.rm=TRUE))
```

```{r}
df_gpa_survey_takers %>%
  filter(CumulativeGPA != 0) %>%
  group_by(GradeLevelID.x) %>%
  summarize(n = n(),
            MeanGPA = mean(CumulativeGPA, na.rm=TRUE))
```

```{r}
gpa_by_dosage <- df_gpa_survey_takers %>%
  filter(CumulativeGPA != 0) %>%
  group_by(GradeLevelID.x,
           CRDoseGroup) %>%
  summarize(n = n(),
            MeanGPA = mean(CumulativeGPA, na.rm=TRUE))

gpa_by_dosage
```


# Tests on dosage

```{r}
df_gpa_survey_takers %>%
  filter(CumulativeGPA != 0) %>%
  ggplot() +
  geom_histogram(aes(x = CumulativeGPA)) +
  facet_grid(CRDoseGroup ~ GradeLevelID.x)
```

The histograms don't appear to be Normally distributed, so we will use a Shapiro-Wilk test to test for Normality.

```{r shapiro_gpa}
shapiro_gpa <- list()
pval_shapiro_gpa <- c()

for (i in 2:4) {
  
  shapiro_gpa[[i]] <- df_gpa_survey_takers %>%
    filter(CumulativeGPA != 0,
           GradeLevelID.x == i + 8) %>%
    pull(CumulativeGPA) %>%
    shapiro.test()
  
  pval_shapiro_gpa[i] <- unlist(shapiro_gpa[[i]]$p.value)
  
}

print(pval_shapiro_gpa)
```

The 12th grade p-value is above 0.05 (0.39 > 0.05), so the 12th grade distribution seems to be Normally distributed, while the 10th and 11th grade distributions (0.07, 0.02) appear to be weakly and non-Normal, respectively.

To be safe, we'll use non-parametric tests to compare the GPA distributions by dosage.

H0: Students with a higher dosage have the same GPA as those with a lower dosage.
HA: Students with a higher dosage have a higher GPA as those with a lower dosage.

```{r mann_whitney_gpa, warning=FALSE}
mann_whitney_gpa <- list()
pval_mann_whitney_gpa <- c()

for (i in 2:4) {
  
  mann_whitney_gpa[[i]] <- wilcox.test(CumulativeGPA ~ CRDoseGroup,
                                       data = df_gpa_survey_takers %>%
                                         filter(CumulativeGPA != 0),
                                       subset = GradeLevelID.x == i+8,
                                       alternative = "less")
  pval_mann_whitney_gpa[i] <- unlist(mann_whitney_gpa[[i]]$p.value)
  
}

print(pval_mann_whitney_gpa)
```

