---
title: "Survey_Item_Analysis"
author: "AO"
date: "6/23/2022"
output: html_document
---

Academy - Create student level CNI and SLSS composite scores (i.e., average across all CNI or SLSS scores grouped by student)
```{r}

ac_survey_composites <- ac_survey_clean%>%
  rowwise()%>%
  mutate(CNI_Std_Mean = mean(c_across(starts_with("CNI")), na.rm = T),
        SLSS_Std_Mean = mean(c_across(starts_with("SLSS")), na.rm = T)) %>%
  ungroup()
#write_csv("~/Github/Camp-Rio-Year-3-21-22-/data/AC_survey_composites.csv")
#write.csv(ac_survey_composites, "AC_survey_composites.csv")

```

Academy - Create overall mean CNI, SLSS
```{r}
#mutate will keep all collumns, summarize will create a new df with only the new summary columns
ac_survey_mean <- ac_survey_composites %>%
  summarize(CNI_all_Mean = mean(CNI_Std_Mean),
         SLSS_all_Mean = mean(SLSS_Std_Mean))

#write.csv(ac_survey_mean, "~/Github/Camp-Rio-Year-3-21-22-/data/ac_survey_overall_mean.csv")

```

Academy - Create CNI and SLSS mean by grade level
```{r}

ac_survey_grdlvl_mean <- ac_survey_composites %>%
  group_by(GradeLevel) %>%
  summarize(CNI_GRD_Mean = mean(CNI_Std_Mean),
         SLSS_GRD_Mean = mean(SLSS_Std_Mean))

#write.csv(ac_survey_grdlvl_mean, "~/Github/Camp-Rio-Year-3-21-22-/data/ac_survey_by_grdlvl.csv")
```


Academy - Create CNI and SLSS mean by dose level
```{r}
ac_survey_dose_mean <- ac_survey_composites %>%
  group_by(Dose_groups) %>%
  summarize(CNI_dose_Mean = mean(CNI_Std_Mean),
         SLSS_dose_Mean = mean(SLSS_Std_Mean))

write.csv(ac_survey_dose_mean, "~/Github/Camp-Rio-Year-3-21-22-/data/ac_survey_mean_by_dosegroup.csv")
```

College Prep - Create student level NR6 and SLSS composite scores (i.e., average across all CNI or SLSS scores grouped by student)
```{r}
CP_survey_composites <- CP_survey_clean%>%
  rowwise()%>%
  mutate(NR6_Std_Mean = mean(c_across(starts_with("NR6")), na.rm = T),
        SLSS_Std_Mean = mean(c_across(starts_with("SLSS")), na.rm = T)) %>%
  ungroup()
write.csv(CP_survey_composites, "~/Github/Camp-Rio-Year-3-21-22-/data/CP_survey_composites.csv")
```

College Prep - Create overall mean NR6, SLSS
```{r}
#mutate will keep all collumns, summarize will create a new df with only the new summary columns
CP_survey_mean <- CP_survey_composites %>%
  summarize(NR6_all_Mean = mean(NR6_Std_Mean),
         SLSS_all_Mean = mean(SLSS_Std_Mean))
#write.csv(CP_survey_mean, "~/Github/Camp-Rio-Year-3-21-22-/data/CP_survey_mean.csv")
```

College Prep - Create CNI and SLSS mean by grade level
```{r}

CP_survey_grdlvl_mean <- CP_survey_composites %>%
  group_by(GradeLevel) %>%
  summarize(NR6_GRD_Mean = mean(NR6_Std_Mean),
         SLSS_GRD_Mean = mean(SLSS_Std_Mean))

#write.csv(CP_survey_grdlvl_mean, "~/Github/Camp-Rio-Year-3-21-22-/data/CP_survey_mean_by_grdlvl.csv")
```

College Prep - CNI & SLSS mean by grade group
```{r}
CP_survey_grdgroup_mean <- CP_survey_composites %>%
  group_by(Grd_groups) %>%
  summarize(NR6_GRD_Mean = mean(NR6_Std_Mean),
         SLSS_GRD_Mean = mean(SLSS_Std_Mean))

#write.csv(CP_survey_grdgroup_mean, "~/Github/Camp-Rio-Year-3-21-22-/data/CP_survey_mean_by_grdgroup.csv")

```


College Prep - Create NR6 and SLSS mean by dose level
```{r}
CP_survey_Doselevel_mean <- CP_survey_composites %>%
  group_by(Dose_levels) %>%
  summarize(NR6_GRD_Mean = mean(NR6_Std_Mean),
         SLSS_GRD_Mean = mean(SLSS_Std_Mean))

write.csv(CP_survey_grdgroup_mean, "~/Github/Camp-Rio-Year-3-21-22-/data/CP_survey_mean_by_doselevel.csv")
```

summary
unique(ac_survey_clean$CR_2)
[1] "Slightly interested"   "Quite interested"      "Extremely interested"  "Not at all interested"
[5] "Somewhat interested"  

