---
title: "NSC analysis"
output: html_notebook
---

## Notebook setup

* Filename: 06-nsc-analysis.Rmd
* Path: src/06-nsc-analysis.Rmd
* Author: Steven Macapagal
* Date created: 2022-06-22
* Date modified: 2022-06-22
* Purpose: This notebook preps and conducts analysis for NSC data for Question 3.
* Inputs: df_nsc
* Outputs: 
* Notes:

# Survey analysis

counted 77 students who were surveyed in 2020-2021 (5.8 %)
```{r}
df_nsc %>%
  group_by(StudentNumber) %>%
  mutate(row_number = row_number()) %>%
  filter(row_number == max(row_number, na.rm = TRUE)) %>%
  ungroup() %>%
  count(Surveyed)
```

distribution of enrollment statuses:

* F = 852
* Q = 194
* H = 87
* L = 61
* W = 73
* A = 2
* NA = 131
```{r}
df_nsc %>%
  group_by(StudentNumber) %>%
  mutate(row_number = row_number()) %>%
  filter(row_number == max(row_number, na.rm = TRUE)) %>%
  ungroup() %>%
  count(EnrollmentStatus)
```


distribution of enrollment among survey takers:

* F = 51
* Q = 11
* H = 2
* L = 1
* W = 3
* NA = 9

if we assume all NAs are W, then 84.4 % of those surveyed had an active enrollment as their last record

if we assume all NAs are at least L, then 96.2 % of those surveyed had an active enrollment as their last record
```{r}
df_nsc %>%
  group_by(StudentNumber) %>%
  mutate(row_number = row_number()) %>%
  filter(row_number == max(row_number, na.rm = TRUE),
         Surveyed == 1) %>%
  ungroup() %>%
  count(EnrollmentStatus)
```


