---
title: "NSC analysis"
output: html_notebook
---

## Notebook setup

* Filename: 06-nsc-analysis.Rmd
* Path: src/06-nsc-analysis.Rmd
* Author: Steven Macapagal
* Date created: 2022-06-22
* Date modified: 2022-07-12
* Purpose: This notebook preps and conducts analysis for NSC data for Question 3.
* Inputs: df_nsc
* Outputs: 
* Notes:

# Survey analysis

counted 77 students who were surveyed in 2020-2021 (5.8 %)
```{r}
df_nsc %>%
  group_by(StudentNumber) %>%
  mutate(row_number = row_number()) %>%
  filter(row_number == max(row_number, na.rm = TRUE)) %>%
  ungroup() %>%
  count(Surveyed)
```

distribution of enrollment statuses:

* F = 852
* Q = 194
* H = 87
* L = 61
* W = 73
* A = 2
* NA = 131
```{r}
df_nsc %>%
  group_by(StudentNumber) %>%
  mutate(row_number = row_number()) %>%
  filter(row_number == max(row_number, na.rm = TRUE)) %>%
  ungroup() %>%
  count(EnrollmentStatus)
```


distribution of enrollment among survey takers:

* F = 51
* Q = 11
* H = 2
* L = 1
* W = 3
* NA = 9

if we assume all NAs are W, then 84.4 % of those surveyed had an active enrollment as their last record

if we assume all NAs are at least L, then 96.2 % of those surveyed had an active enrollment as their last record
```{r}
df_nsc %>%
  group_by(StudentNumber) %>%
  mutate(row_number = row_number()) %>%
  filter(row_number == max(row_number, na.rm = TRUE),
         Surveyed == 1) %>%
  ungroup() %>%
  count(EnrollmentStatus)
```

Distribution of each student's first enrollment month:

* May = 4
* June = 1
* August = 1227
* September = 75
* October = 1
* December = 1
* January = 5

```{r}
df_nsc %>%
  ungroup() %>%
  filter(Order == 1) %>%
  mutate(month = month(EnrollmentBegin)) %>%
  count(month)
```

Distribution of first enrollments

* F = 898
* Q = 189
* H = 80
* L = 46
* W = 57
* A = 1
* NA = 129

Note that some of these students enrolled in the summer, so their first-time enrollment may not be full-time.

```{r}
df_nsc %>%
  ungroup() %>%
  filter(CollegeSequence == 1) %>%
  count(EnrollmentStatus)
```


## Matriculation according to Camp Rio

There were 435 2021 seniors who attended Camp Rio and 933 who did not.

```{r}
df_nsc %>%
  filter(year(EnrollmentEnd) == 2021,
         month(EnrollmentEnd) == max(month(EnrollmentEnd))) %>%
  group_by(Attended) %>%
  summarize(n = n())
```

If we aggregate all enrollment with status at least "L" and remove all NA enrollments, then we get these distributions:

**Did Not Attend**

* Above "L" = 857/891 = 96.2%
* "W" or "A" = 34/891 = 3.8%

**Attended**

* Above "L" = 909/931 = 97.6%
* "W" or "A" = 22/931 = 2.4%

```{r}
table_cr_matric_long <- df_nsc %>%
  filter(year(EnrollmentEnd) == 2021,
         month(EnrollmentEnd) == max(month(EnrollmentEnd))) %>%
  group_by(Attended, EnrollmentStatus) %>%
  summarize(n = n())

table_cr_matric_wide <- table_cr_matric_long %>%
  mutate(EnrollmentStatus = fct_collapse(EnrollmentStatus,
                                         SomeCollege = c("F", "Q", "H", "L"),
                                         Withdrew = c("W", "A"))) %>%
  group_by(Attended, EnrollmentStatus) %>%
  summarize(n = sum(n)) %>%
  filter(!is.na(EnrollmentStatus)) %>%
  pivot_wider(names_from = EnrollmentStatus,
              values_from = n)
```

Now, we will conduct a chi-square test of independence.

* H0: Camp Rio attendance and college matriculation are independent.
* HA: Not.

```{r}
chisq_test_matric <- table_cr_matric_wide %>%
  column_to_rownames(var = "Attended") %>%
  as.matrix() %>%
  chisq.test()

chisq_stat_matric <- chisq_test_matric$statistic
pval_matric <- chisq_test_matric$p.value
```

The chi-square stat of `r chisq_stat_matric` with df = 1, has a p-value of `r pval_matric`, which is greater than 0.05. We fail to reject the null and conclude there is not enough evidence to suggest Camp Rio attendance and college matriculation are dependent.
