---
title: "AP Science Analysis"
output: html_notebook
---

## Notebook setup

* Filename: 08-ap-analysis.Rmd
* Path: src/08-ap-analysis.Rmd
* Author: Steven Macapagal
* Date created: 2022-07-19
* Date modified: 2022-07-19
* Purpose: This notebook preps and conducts analysis for AP scores for Question 3.
* Inputs: df_ap_attendees, df_ap_survey_takers
* Outputs: 
* Notes:


```{r}
df_ap_survey_takers %>% 
  filter(ExamName %in% c("Biology", "Environmental Science", "Chemistry", "Physics 1")) %>%
  group_by(ExamName) %>% 
  count(AP_Result) %>% 
  mutate(Percent = scales::label_percent(accuracy = 0.1)(n / sum(n)))
```

```{r}
df_ap_survey_takers %>%   
  filter(ExamName %in% c("Biology", "Environmental Science", "Chemistry", "Physics 1"), 
         AdminYear == "22") %>% 
  group_by(ExamName) %>%
  summarize(MeanAPScore = mean(AP_Result, na.rm = TRUE),
            SDAPScore = sd(AP_Result, na.rm = TRUE))
```

```{r}
df_ap_survey_takers %>%   
  filter(ExamName %in% c("Biology", "Environmental Science", "Chemistry", "Physics 1"), 
         AdminYear == "22") %>% 
  group_by(CRDoseGroup) %>%
  summarize(MeanAPScore = mean(AP_Result, na.rm = TRUE),
            SDAPScore = sd(AP_Result, na.rm = TRUE),
            n = n())
```

```{r}
df_ap_survey_takers %>%
  filter(ExamName %in% c("Biology", "Environmental Science", "Chemistry", "Physics 1"), 
         AdminYear == "22") %>%
  mutate(PassedExam = if_else(AP_Result %in% c(3, 4, 5), "Scored 3+", "Scored Below 3")) %>%
  group_by(PassedExam) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(PercentPassed = n / sum(n))
```


```{r}
df_ap_survey_takers %>% 
  filter(ExamName %in% c("Biology", "Environmental Science", "Chemistry", "Physics 1"), 
         AdminYear == "22") %>%
  mutate(PassedExam = if_else(AP_Result %in% c(3, 4, 5), "Scored 3+", "Scored Below 3")) %>%
  group_by(ExamName, PassedExam) %>%
  summarize(n = n()) %>%
  # ungroup() %>%
  mutate(PercentPassed = n / sum(n))
```

```{r}
df_ap_survey_takers %>%
  filter(ExamName %in% c("Biology", "Environmental Science", "Chemistry", "Physics 1"), 
         AdminYear == "22") %>%
  mutate(PassedExam = if_else(AP_Result %in% c(3, 4, 5), "Scored 3+", "Scored Below 3")) %>%
  group_by(ExamName, PassedExam) %>%
  summarize(n = n()) %>%
  # ungroup() %>%
  mutate(PercentPassed = n / sum(n))
```

## Distributions by dosage

Excluding Chemistry due to low intake, Physics because no one passed. (Traditionally what happens). This has not significantly changed the overall story of the distributions.

```{r}
df_ap_survey_takers %>%
  filter(ExamName %in% c("Biology", "Environmental Science"), 
         AdminYear == "22") %>%
  mutate(PassedExam = if_else(AP_Result %in% c(3, 4, 5), "Scored 3+", "Scored Below 3")) %>%
  group_by(PassedExam, CRDoseGroup) %>%
  summarize(n = n()) %>%
  # ungroup() %>%
  mutate(PercentPassed = n / sum(n)) %>%
  pivot_wider(names_from = CRDoseGroup,
              values_from = c(n, PercentPassed))
```


## Tests on pass rates

Because $n_{\rm Scored 3+}$ is so small, we should use a Fisher exact test to test the differences in proportions.

* H0: The proportion of those who pass and had a high dose perform at the same rate as those who pass and had a low dose.
* HA: Not.

```{r}
(pval_fisher_ap <- 1 - phyper(q = 15 - 1, 
                              m = 15 + 3, 
                              n = 34 + 55, 
                              k = 15 + 34))

```

Because the p-value `r pval_fisher_ap` < 0.05, we reject H0. There is significant evidence that AP pass rates are different by dosage.